chronologies

### 2018-05-07 analysis/chronos/analysis_chronologies.Rmd
update analysis chrono
export data comparison bais chronos

correla %>% 
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2)  +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) + 
  facet_wrap(~metodo_correla, ncol=2) +
  theme(strip.background = element_blank())
```

>>>>

write.csv(correla, file=paste(di, "data/correla_ventanas_temporales/correla.csv", sep=""), row.names = FALSE)

correla %>% 
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2)  +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) + 
  facet_wrap(~metodo_correla, ncol=2) +
  theme(strip.background = element_blank())
